---
title: "prediction"
output: html_document
date: "2023-01-02"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Import the necessary packages

```{r message=FALSE, warning=FALSE, include=FALSE}
library(ggplot2)
library(dplyr)
library(tidyr)
library(patchwork)
library(caret)
library(e1071)
library(randomForest)
library(Metrics)
library(ggcorrplot)
library(xgboost)
library(tidyverse)       
library(olsrr)      
library(kernlab)
```

# Exploring data set

#### Loading data set

```{r message=FALSE, warning=FALSE}
# Load the data
data <- read.csv("insurance_data.csv")

# Get a summary of the data
summary(data)
```

#### Cleaning data set

```{r message=FALSE, warning=FALSE}
# checking if there are missing values 
sum(is.na(data))
```

There is no missing values in the data set

#### Visualizing data set

AGE

```{r message=FALSE, warning=FALSE}
# plotting age
p_age <- data %>% 
  ggplot() + aes(x = age) + 
  geom_bar(fill = "dodgerblue3", color = "black", alpha = 0.6) +   
  labs(title = 'age', y = 'count') +
  geom_vline(xintercept = min(data$age), linetype = "dashed", color = "red") +
  geom_text(x = min(data$age), y = 0, label = min(data$age), vjust = 0, size=12) +
  geom_vline(xintercept = max(data$age), linetype = "dashed", color = "red") +
  geom_text(x = max(data$age), y = 0, label = max(data$age), vjust = 0, size=12) +
  theme_classic() +
  theme(text=element_text(family="Times"),
        plot.title = element_text(hjust = 0.5, size=40),
			  axis.title.x=element_blank(),
			  axis.title.y= element_text(size=35),
			  axis.text.x = element_text(size=35),
			  axis.text.y = element_text(size=35))

# Divide the ages into intervals of 5 years
# new_data$age <- cut(data$age, breaks = seq(min(data$age)-1, max(data$age)+10, by = 10))

# plotting new age 
# p_new_age1 <- new_data %>% 
#   mutate(across(c(age),as.factor)) %>% 
#   group_by(age) %>% 
#   summarise(n = n()) %>% 
#   ggplot() +
#   aes(x = age, y = n, fill = age) +
#   geom_col(position = "dodge") +
#   geom_text(aes(age, n, label = n, group = age), 
#             hjust = 0.5,
#             position = position_dodge(width = -1)) +
#   scale_x_discrete(limits = rev(levels(new_data$age))) +
#   # guides(fill = "none") + 
#   labs(title = '2. Age in intervals') +
#   theme(plot.title = element_text(hjust = 0.5),
# 			  axis.title.x=element_blank(),
#         axis.text.x=element_blank(),
#         axis.ticks.x=element_blank(),
# 			  axis.title.y=element_blank(),
#         axis.ticks.y=element_blank())

# label encoding
# new_data$age <- as.numeric(factor(new_data$age))

# plotting new age 
# p_new_age2 <- new_data %>% 
#   mutate(across(c(age),as.factor)) %>% 
#   group_by(age) %>% 
#   summarise(n = n()) %>% 
#   ggplot() +
#   aes(x = age, y = n, fill = age) +
#   geom_col(position = "dodge") +
#   geom_text(aes(age, n, label = n, group = age), hjust = 0.5, position = position_dodge(width = -1)) +
#   scale_x_discrete(limits = rev(levels(new_data$age))) +
#   # guides(fill = "none") + 
#   labs(title = '3. Label encoding') +
#   theme(plot.title = element_text(hjust = 0.5),
# 			  axis.title.x=element_blank(),
#         axis.text.x=element_blank(),
#         axis.ticks.x=element_blank(),
# 			  axis.title.y=element_blank(),
#         axis.ticks.y=element_blank())
# plots
# p_age | p_new_age1 | p_new_age2
p_age
```

SEX

```{r message=FALSE, warning=FALSE}
# plotting sex
p_sex <- data %>% 
  ggplot() + 
  aes(x = sex) + 
  geom_bar(fill = "dodgerblue3", color = "black", alpha = 0.7) +   
  labs(title = 'sex', y = 'count') +
  theme_classic() +
  theme(text=element_text(family="Times"),
        plot.title = element_text(hjust = 0.5, size=40),
			  axis.title.x=element_blank(),
			  axis.title.y= element_text(size=35),
			  axis.text.x = element_text(size=35),
			  axis.text.y = element_text(size=35))

p_sex
```

BMI

```{r message=FALSE, warning=FALSE}
# plotting bmi
p_bmi <- data %>% 
  ggplot() + 
  aes(x = bmi) + 
  geom_density(color = "dodgerblue4", fill="dodgerblue3", width = 50, alpha = 0.7) + 
  geom_vline(xintercept = min(data$bmi), linetype = "dashed", color = "red") +
  geom_text(x = min(data$bmi), y = 0, label = min(data$bmi), vjust = 0, size = 10) +
  geom_vline(xintercept = max(data$bmi), linetype = "dashed", color = "red") +
  geom_text(x = max(data$bmi), y = 0, label = max(data$bmi), vjust = 0, size = 10) +
  labs(title = 'bmi') +
  theme_classic() +
  theme(text=element_text(family="Times"),
        plot.title = element_text(hjust = 0.5, size=40),
			  axis.title.x=element_blank(),
			  axis.title.y= element_text(size=35),
			  axis.text.x = element_text(size=35),
			  axis.text.y = element_text(size=35))

p_bmi
```

CHILDREN

```{r message=FALSE, warning=FALSE}
# plotting children
p_children <- data %>% 
  ggplot() + 
  aes(x = children) + 
  geom_bar(fill = "dodgerblue3", color = "black", alpha = 0.7) +   
  labs(title = 'children', y = 'count') +
  theme_classic() +
  theme(text=element_text(family="Times"),
      plot.title = element_text(hjust = 0.5, size=40),
		  axis.title.x=element_blank(),
		  axis.title.y= element_text(size=35),
		  axis.text.x = element_text(size=35),
		  axis.text.y = element_text(size=35))

p_children
```

SMOKER

```{r}
# plot smoker
p_smoker <- data %>% 
  ggplot() + aes(x = smoker) + 
  geom_bar(fill = "dodgerblue3", color = "black", alpha = 0.7) +   
  labs(title = 'smoker', y = 'count') +
  theme_classic() +
   theme(text=element_text(family="Times"),
        plot.title = element_text(hjust = 0.5, size=40),
			  axis.title.x=element_blank(),
			  axis.title.y= element_text(size=35),
			  axis.text.x = element_text(size=35),
			  axis.text.y = element_text(size=35))

p_smoker
```

REGION

```{r}
# plotting region
p_region <- data %>% 
  ggplot() + 
  aes(x = region) + 
  geom_bar(fill = "dodgerblue3", color = "black", alpha = 0.7) +   
  labs(title = 'region', y = 'count') +
  coord_flip() +
  theme_classic() +
  theme(text=element_text(family="Times"),
        plot.title = element_text(hjust = 0.5, size=40),
  		  axis.title.x=element_blank(),
  		  axis.title.y= element_text(size=35),
  		  axis.text.x = element_text(size=35),
  		  axis.text.y = element_text(size=35))
p_region
```

CHARGES

```{r message=FALSE, warning=FALSE}
# plotting bmi
p_charges <- data %>% 
  ggplot() + 
  aes(x = charges) + 
  geom_density(color = "dodgerblue4", fill="dodgerblue3", width = 50, alpha = 0.7) + 
  geom_vline(xintercept = min(data$charges), linetype = "dashed", color = "red") +
  geom_text(x = min(data$charges), y = 0, label = round(min(data$charges),2), vjust = 0, size = 10) +
  geom_vline(xintercept = max(data$charges), linetype = "dashed", color = "red") +
  geom_text(x = max(data$charges), y = 0, label = round(max(data$charges),2), vjust = 0, size = 10) +
  labs(title = 'charges') +
  theme_classic() +
  theme(text=element_text(family="Times"),
        plot.title = element_text(hjust = 0.5, size=40),
  		  axis.title.x=element_blank(),
  		  axis.title.y= element_text(size=35),
  		  axis.text.x = element_text(size=35, angle = 10),
  		  axis.text.y = element_text(size=35))

p_charges
```

#### Checking outliers in the columns: "age", "bmi" and "charges"

```{r}
# Checking Outliers
data %>% 
  select(bmi, age, charges) %>% 
  log() %>% 
  pivot_longer(c(bmi, age, charges)) %>%
  ggplot(aes(x=name,y=value,fill=name), alpha = 0.7) +
  geom_boxplot() +
  labs(title="Boxplot for age, bmi and charges") +
  theme_classic() +
  theme(text=element_text(family="Times"),
        plot.title = element_text(hjust = 0.5, size=35),
  		  axis.title.x=element_blank(),
  		  axis.title.y= element_text(size=35),
  		  axis.text.x = element_text(size=35),
  		  axis.text.y = element_text(size=35),
			  legend.position = "none")
```

#### Removing outliers for "bmi"

```{r}
# Removing Outliers (method1)
quartiles <- quantile(data$bmi, probs=c(.25, .75), na.rm = FALSE)
IQR <- IQR(data$bmi)

Lower <- quartiles[1] - 1.03 * IQR
Upper <- quartiles[2] + 2.1 *IQR

data <- subset(data, data$bmi > Lower & data$bmi < Upper)
 
# Removing Outliers (method2)
# new_data_no_outlier <- new_data[-which(new_data$bmi %in% boxplot.stats(new_data$bmi)$out), ]

# Checking Outliers
data %>% 
  select(bmi, age, charges) %>% 
  log() %>% 
  pivot_longer(c(bmi, age, charges)) %>%
  ggplot(aes(x=name,y=value,fill=name), alpha = 0.7) +
  geom_boxplot() +
  labs(title="Boxplot for age, bmi and charges") +
  theme_classic() +
  theme(text=element_text(family="Times"),
        plot.title = element_text(hjust = 0.5, size=35),
  		  axis.title.x=element_blank(),
  		  axis.title.y= element_text(size=35),
  		  axis.text.x = element_text(size=35),
  		  axis.text.y = element_text(size=35),
			  legend.position = "none")
```

# Exploring relationships in data set

#### Is there any relation between *charges* and *bmi*?

```{r}
# plot(data$bmi, data$charges, pch = 1, cex = 1, col = "blue", main = "Charge vs bmi", xlab = "Body Mass Index", ylab = "Insurance charges")
# abline(lm(data$charges ~ data$bmi))

plot <- data %>% 
        ggplot(aes(bmi, charges)) +
        geom_point(color = "dodgerblue3", alpha = 0.3) +
        geom_smooth(method = "lm", color = "dodgerblue4") +
        labs(title = 'charges vs bmi', x = "Bmi", y = "Insurance charges") +
        theme_classic() +
        theme(text=element_text(family="Times"),
                plot.title = element_text(hjust = 0.5, size=30),
        			  axis.title.x= element_text(size=25),
        			  axis.title.y= element_text(size=25),
        			  axis.text.x = element_text(size=30),
        			  axis.text.y = element_text(size=30, angle=60))
plot
```

#### Is there any relation between *charges* and *age*?

```{r}
# plot(data$age, data$charges, pch = 1, cex = 1, col = "blue", main = "Charge vs age", xlab = "Age", ylab = "Insurance charges")
# abline(lm(data$charges ~ data$age))

plot <- data %>% 
        mutate(smoker = as.factor(smoker)) %>% 
        ggplot(aes(age, charges)) +
        geom_point(color = "dodgerblue3", alpha = 0.3) +
        geom_smooth(method = "lm", color = "dodgerblue4") +
        labs(title = 'charges vs age', x = "Age", y = "Insurance charges") +
        theme_classic() +
        theme(text=element_text(family="Times"),
                plot.title = element_text(hjust = 0.5, size=30),
        			  axis.title.x= element_text(size=25),
        			  axis.title.y= element_text(size=25),
        			  axis.text.x = element_text(size=30),
        			  axis.text.y = element_text(size=30, angle=60))
plot
```

#### Is there any relation between *charges* and *smoker*?

```{r}
# plot(new_data$smoker, new_data$charges, pch = 1, cex = 1, col = "blue", main = "Charge vs smoker", xlab = "Smoker", ylab = "Insurance charges")
# abline(lm(new_data$charges ~ new_data$smoker))

plot <- data %>% 
  ggplot(aes(smoker, charges)) +
  geom_point(color = "dodgerblue3", alpha = 0.3, size = 2) +
  geom_smooth(method = "lm", color = "dodgerblue4") +
  labs(title = 'charges vs smoker', x = "Smoker", y = "Insurance charges") +
  theme_classic() +
  theme(text=element_text(family="Times"),
                plot.title = element_text(hjust = 0.5, size=30),
        			  axis.title.x= element_text(size=25),
        			  axis.title.y= element_text(size=25),
        			  axis.text.x = element_text(size=30),
        			  axis.text.y = element_text(size=30, angle=60))
plot
```

```{r}
plot <- data %>% 
        mutate(smoker = as.factor(smoker)) %>% 
          ggplot(aes(age, charges, color = smoker)) +
          geom_point(alpha = 0.1, size = 2) +
          geom_smooth(method = "lm", se = FALSE) +
          scale_color_manual(values = c("dodgerblue", "dodgerblue4")) +
          labs(title = 'charges vs age vs smoker', x = "Age", y = "Insurance charges") +
          theme_classic() +
          theme(text=element_text(family="Times"),
                plot.title = element_text(hjust = 0.5, size=30),
        			  axis.title.x= element_text(size=25),
        			  axis.title.y= element_text(size=25),
        			  axis.text.x = element_text(size=30),
        			  axis.text.y = element_text(size=30, angle=60),
        			  legend.title = element_text(size = 30),
        			  legend.text = element_text(size = 30),
        			  legend.position = "right")
plot
```

#### Correlation matrix

```{r}

cor_data <- data
cor_data$sex <- as.numeric(as.factor(cor_data$sex))
cor_data$smoker <- as.numeric(as.factor(cor_data$smoker))
cor_data$region <- as.numeric(as.factor(cor_data$region))
cor_data$age <- as.numeric(cor_data$age)
cor_data$bmi <- as.numeric(cor_data$bmi)

cormat <-cor(cor_data, method = "pearson")

# Get lower triangle of the correlation matrix
  get_lower_tri<-function(cormat){
    cormat[upper.tri(cormat)] <- NA
    return(cormat)
  }
  # Get upper triangle of the correlation matrix
  get_upper_tri <- function(cormat){
    cormat[lower.tri(cormat)]<- NA
    return(cormat)
  }
  
  upper_tri <- get_upper_tri(round(cormat ,2))

# Melt the correlation matrix
library(reshape2)
melted_cormat <- melt(upper_tri, na.rm = TRUE)

# Heatmap
ggheatmap <- ggplot(data = melted_cormat, aes(Var2, Var1, fill = value)) +
    geom_tile(color = "white")+
    scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 0, limit = c(-1,1), space = "Lab", name="Correlation") +
    theme_void() + 
    theme(axis.text.x = element_text(angle = 45, vjust = 1, 
        size = 8, hjust = 1) , axis.text.y = element_text(vjust = 1, 
        size = 8, hjust = 1)) +
    coord_fixed() + 
    geom_text(aes(Var2, Var1, label = value), color = "black", size = 3.5) +
    labs(title="Correlation matrix") +
    theme(text=element_text(family="Times"),
          plot.title = element_text(hjust = 0.5, size=15),
    		  axis.title.x= element_blank(),
    		  axis.title.y= element_blank(),
    		  axis.text.x = element_text(size=13),
    		  axis.text.y = element_text(size=13),
          panel.grid.major = element_blank(),
          panel.border = element_blank(),
          legend.justification = c(1, 0),
          legend.position = c(1.5, 1.5),
          legend.direction = "horizontal")+
          guides(fill = guide_colorbar(barwidth = 7, barheight = 1,
                        title.position = "top", title.hjust = 0.5))
ggheatmap
```

#### Statistical significance of these relationships

```{r}
# Extract the names of the variables
names <- colnames(cor_data)

# Loop through the variables and compute the p-values
p_values <- matrix(NA, nrow = length(names), ncol = length(names))
for (i in 1:length(names)) {
  for (j in 1:length(names)) {
    # Skip the diagonal (i.e., the correlation of a variable with itself)
    if (i == j) {
      next
    }
    # Compute the p-value
    result <- cor.test(cor_data[, i], cor_data[, j])
    p_values[i, j] <- round(result$p.value, digits = 2)
  }
}

# Print the p-values
print(p_values)
```

We can see that there is correlation between the target (charges) and the variables age, smoker and bmi.

# Feature engineering

#### Label encoding of the columns: "sex" and "smoker"

```{r}
library(superml)

new_data <- data

# create a label encoder object
encoder = superml::LabelEncoder$new()
# fitting and transforming the data
new_data$sex <- encoder$fit_transform(new_data$sex)

# create a label encoder object
encoder = superml::LabelEncoder$new()
# fitting and transforming the data
new_data$smoker <- encoder$fit_transform(new_data$smoker)
```

#### One-hot encoding of the column: "region"

```{r}
#define one-hot encoding function
dummy <- caret::dummyVars(" ~ .", data=new_data)
#perform one-hot encoding on data frame
new_data <- data.frame(predict(dummy, newdata=new_data))

# Drop the "country" column
new_data <- new_data %>% select(-regionsouthwest)
```

#### Transforming values into intervals and encode the label: "age" and "bmi":

After trying on some models later on, we noticed that we get better result without using standardization.

```{r}
# # Divide the ages into intervals of 10 years
# new_data$age <- cut(data$age, breaks = seq(min(data$age)-1, max(data$age)+10, by = 10))
# # label encoding
# new_data$age <- as.numeric(factor(new_data$age))

# # Divide the bmis into intervals of 10
# new_data$bmi <- cut(data$bmi, breaks = seq(min(data$bmi)-1, max(data$bmi)+10, by = 10))
# # label encoding
# new_data$bmi <- as.numeric(factor(new_data$bmi))
```

```{r}
head(new_data)
```

#### Splitting the data into train and test set

```{r}
# Get the index of the "charges" column
charges_index <- which(names(new_data) == "charges")

# Splitting the dataset into training and test sets 
set.seed(123)
train_index <- createDataPartition(new_data$charges, p=0.70, list=FALSE)
X_train <- new_data[train_index, -charges_index]
y_train <- new_data[train_index, charges_index]
X_test <- new_data[-train_index, -charges_index]
y_test <- new_data[-train_index, charges_index]

# delete indices in the dataframes 
row.names(X_train) <- NULL
row.names(X_test) <- NULL
```

#### Normalization of the data

```{r}
# Normalize the data using Min-Max scaling
process <- preProcess(X_train, method='range')
X_train <- predict(process, X_train)
process <- preProcess(X_test, method='range')
X_test <- predict(process, X_test)
```

#### Standardization of the data

After trying on some models later on, we noticed that we get better result without using standardization.

```{r}
# process <- preProcess(X_train, method=c("center", "scale"))
# X_train <- predict(process, X_train)
# process <- preProcess(X_test, method=c("center", "scale"))
# X_test <- predict(process, X_test)
```

```{r}
head(X_train)
```

# Metrics

#### Function to test the performance of the regression model

```{r}
regression_test <- function(pred, y) {
  # Compute performance metrics
  rmse <- sqrt(mean((pred - y)^2))
  #r2 <- cor(pred, y)^2
  r2 <- 1 - (sum((pred - y)^2)) / (sum((pred - mean(y))^2))
  mae <- mean(abs(pred - y))
  # Print the performance metrics
  print(paste("RMSE      :", rmse))
  print(paste("R-squared :", r2))
  print(paste("MAE       :", mae))
}
```

#### Function to plot the comparison of the predictions of a model and the true values on the testing data

```{r}
performance_plot1 <- function(pred, y) {
  # Create the residuals data that contain the predictions values and the ground truth values for the plotting 
  residuals <- data.frame(
    predictions = pred,
    ground_truth = y
  )
  # plot 
  ggplot(residuals, aes(predictions, ground_truth)) +
      geom_point(color = "dodgerblue2", alpha = 0.7) +
      geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "dodgerblue4") +
      labs(title = 'Predictions vs. True Values', x = "Predictions", y = "True values") +
      theme_classic() +
      theme(text=element_text(family="Times"),
            plot.title = element_text(hjust = 0.5, size=25),
    			  axis.title.x = element_text(size=20),
    			  axis.title.y = element_text(size=20),
    			  axis.text.x = element_text(size=20),
    			  axis.text.y = element_text(size=20, angle=60))
}

performance_plot2 <- function(pred, y) {
  # Create the residuals data that contain the predictions values and the ground truth values for the plotting 
  residuals <- data.frame(
    predictions = pred,
    ground_truth = y
  )
  # plot 
  ggplot(residuals, aes(x = 1:nrow(residuals), y = predictions - ground_truth)) +
      geom_point(color = "dodgerblue2", alpha = 0.7) +
      geom_abline(intercept = 0, slope = 0, linetype = "dashed", color = "dodgerblue4") +
      labs(title = 'Residuals', x = "Index", y = "Error") +
      theme_classic() +
      theme(text=element_text(family="Times"),
            plot.title = element_text(hjust = 0.5, size=25),
    			  axis.title.x = element_text(size=20),
    			  axis.title.y = element_text(size=20),
    			  axis.text.x = element_text(size=20),
    			  axis.text.y = element_text(size=20, angle=60))
}
```

#### 

# Linear models

#### MM1 - Multiple linear model on `smoker`, `age`, and `bmi`

```{r}
# Fitting MLR model with predictors TV and Radio 
mm1 <- lm(y_train ~ bmi + smoker + age , data = X_train)

# Take a look on summary of the model
summary(mm1)
```

> 1.  The created model is statistically significant with p-value \<\<\< 0.05
> 2.  From the coefficients section, it is clear that both coefficients (slopes and intercept) are statistically significant since p-value \<\<\< 0.05
> 3.  This model with `bmi`, `smoker` and `age` as predictors explains approximately **73%** variability of the target variable `charges`.
> 4.  Residual standard error for the model is 6143.

```{r}
cat("Performance on Train data:\n")
# Predict the train set using the best model
predictions <- predict(mm1, data = X_train)
# Compute performance metrics
regression_test(predictions, y_train)

cat("\nPerformance on Test data:\n")
# Predict the test set using the best model
predictions <- predict(mm1, newdata = X_test)
# Compute performance metrics
regression_test(predictions, y_test)

performance_plot1(predictions, y_test)
performance_plot2(predictions, y_test)
```

#### MM2 - Multiple linear model on `smoker`, `age`, `bmi`, `sex`, `children` and `region`

```{r}
# Fitting MLR model with predictors TV and Radio 
mm2 <- lm(y_train ~ ., data = X_train)

# Take a look on summary of the model
summary(mm2)
```

> 1.  The created model is statistically significant with p-value \<\<\< 0.05
> 2.  The intercept, bmi, children, smoker, \`age²\` and \`bmi²\` are statistically significant.
> 3.  This model explains approximately **74%** variability of the target variable `charges`.
> 4.  Residual standard error for the model is 6081.

```{r}
cat("Performance on Train data:\n")
# Predict the train set using the best model
predictions <- predict(mm2, data = X_train)
# Compute performance metrics
regression_test(predictions, y_train)

cat("\nPerformance on Test data:\n")
# Predict the test set using the best model
predictions <- predict(mm2, newdata = X_test)
# Compute performance metrics
regression_test(predictions, y_test)

performance_plot1(predictions, y_test)
performance_plot2(predictions, y_test)
```

# Other machine learning models

#### Generating polynomial features within data set

```{r}
new_data <- new_data %>%
  # mutate("age*children" = age * children) %>%
  mutate("age*bmi" = age * bmi) %>%
  # mutate("bmi*childrem" = bmi * children) %>%
  mutate("age²" = age ^ 2) %>%
  mutate("bmi²" = bmi ^ 2) 
  # mutate("children²" = children ^ 2)
```

#### kNN

```{r}
cat("Performance on Train data:\n")
# Define the hyperparameter grid
grid <- expand.grid(k = c(3, 4, 6, 7))
# Train the model using the train function with the tuneGrid argument
model <- train(x = X_train, y = y_train, method = 'knn', tuneGrid = grid, trControl = trainControl(method = 'cv', number = 5, search = "grid"))
# Predict the train set using the best model
predictions <- predict(model, data = X_train)
# Compute performance metrics
regression_test(predictions, y_train)

cat("\nPerformance on Test data:\n")
# Predict the test set using the best model
predictions <- predict(model, newdata = X_test)
# Compute performance metrics
regression_test(predictions, y_test)

performance_plot1(predictions, y_test)
performance_plot2(predictions, y_test)
```

```{r}
print(model$bestTune)
```

#### RF

```{r}
cat("Performance on Train data:\n")
# Define the hyperparameter grid
grid <- data.frame(mtry = c(1, 2, 3, 4, 5, 6, 7, 8))
# Train the model using the train function with the tuneGrid argument
model <- train(x = X_train, y = y_train, method = 'rf', tuneGrid = grid, trControl = trainControl(method = 'cv', number = 5, search = "grid"))
# Predict the train set using the best model
predictions <- predict(model, data = X_train)
# Compute performance metrics
regression_test(predictions, y_train)

cat("\nPerformance on Test data:\n")
# Predict the test set using the best model
predictions <- predict(model, newdata = X_test)
# Compute performance metrics
regression_test(predictions, y_test)

performance_plot1(predictions, y_test)
performance_plot2(predictions, y_test)
```

```{r}
print(model$bestTune)
```

#### SVR

```{r}
cat("Performance on Train data:\n")
# Define the hyperparameter grid
grid <- data.frame(C = c(0.5, 0.6, 0.7, 0.8, 0.9, 1), sigma = c(0.01, 0.05, 0.1, 0.2, 0.3, 0.4))
# Train the model using the train function with the tuneGrid argument
model <- train(x = X_train, y = y_train, method = 'svmRadial', tuneGrid = grid, trControl = trainControl(method = 'cv', number = 5, search = "grid"))
# Predict the train set using the best model
predictions <- predict(model, data = X_train)
# Compute performance metrics
regression_test(predictions, y_train)

cat("\nPerformance on Test data:\n")
# Predict the test set using the best model
predictions <- predict(model, newdata = X_test)
# Compute performance metrics
regression_test(predictions, y_test)

performance_plot1(predictions, y_test)
performance_plot2(predictions, y_test)
```

```{r}
print(model$bestTune)
```

#### XGBoost

```{r}
cat("Performance on Train data:\n")
# Define the hyperparameter grid
grid <- expand.grid(
  lambda = c(2.2, 2.3, 2.4), 
  alpha = c(2.5, 2.6, 2.7), 
  eta = c(0.001, 0.01, 0.1),
  nrounds = c(12, 13, 15))  
# Train the model with hyperparameter tuning
model <- train(x = X_train, y = y_train, method = 'xgbLinear', tuneGrid = grid, trControl = trainControl(method = 'cv', number = 5, search = "grid"))
# Predict the train set using the best model
predictions <- predict(model, data = X_train)
# Compute performance metrics
regression_test(predictions, y_train)


cat("\nPerformance on Test data:\n")
# Predict the test set using the best model
predictions <- predict(model, newdata = X_test)
# Compute performance metrics
regression_test(predictions, y_test)

performance_plot1(predictions, y_test)
performance_plot2(predictions, y_test)
```

```{r}
print(model$bestTune)
```
